|

### 2021-10-05 01-Chp-Background.Rmd
End of day:

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R). This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.

>>>>

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMGCR). This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
